OpenMotion: An open source library for attitude estimation.

### 2016-05-09 Article/main.tex
adding smartphone journal template

\documentclass[conference]{IEEEtran}
% setup page to suit conference specification using fancyhdr
\usepackage{fancyhdr}
\setlength{\paperwidth}{215.9mm}
\setlength{\hoffset}{-9.7mm}
\setlength{\oddsidemargin}{0mm}
\setlength{\textwidth}{184.3mm}
\setlength{\columnsep}{6.3mm}
\setlength{\marginparsep}{0mm}
\setlength{\marginparwidth}{0mm}

\setlength{\paperheight}{279.4mm}
\setlength{\voffset}{-7.4mm}
\setlength{\topmargin}{0mm}
\setlength{\headheight}{0mm}
\setlength{\headsep}{0mm}
\setlength{\topskip}{0mm}
\setlength{\textheight}{235.2mm}
\setlength{\footskip}{12.4mm}

\setlength{\parindent}{1pc}

% If IEEEtran.cls has not been ins

\usepackage{graphics} % for pdf, bitmapped graphics files
\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{subcaption}
\usepackage{multicol}

\hyphenation{op-tical net-works semi-conduc-tor}

 \setlength{\columnsep}{1.0cm}

\begin{document}

 \title{\fontsize{24pt}{10pt}\selectfont\textbf{OpenMotion}: An open source library for attitude estimation.}

\author{\IEEEauthorblockN{Nizar Ouarti}
\IEEEauthorblockA{IPAL (Sorbonne UPMC, CNRS, \\Astar, NUS, UJF, IMT)\\
Singapore\\
Email: nizar.ouarti@ipal.cnrs.fr}
\and
\IEEEauthorblockN{Thomas Braud}
\IEEEauthorblockA{IPAL (Sorbonne UPMC, CNRS,\\ Astar, NUS, UJF, IMT)\\
Singapore\\
Email: braud.thomas@ipal.cnrs.fr }
\and
\IEEEauthorblockN{Vivien Billaud}
\IEEEauthorblockA{IPAL (Sorbonne UPMC, CNRS,\\ Astar, NUS, UJF, IMT)\\
Singapore }}

@@

\thispagestyle{fancy}
\fancyhead{}
\lhead{}
\lfoot{}
\cfoot{}
\rfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\begin{abstract}
The abstract goes here
\end{abstract}

\IEEEpeerreviewmaketitle

@@

@@

\item The object-fixed reference frame $\{c\}$ is a moving and rotating coordinate frame that is fixed to the device. The $x$-axis points in the forward direction, the $y$-axis to the right side and the $z$-axis upward. 
\end{itemize}

We admit that all the components of the IMU belong to the same reference frame $\{c\}$ (ref figure~\ref{Schema_situation}). It is a cyclopean approximation \cite{ouarti2008multimodal} .

@@

@@

A quaternion is a four-dimensional vector, defined as $ \mathbi{q} = \begin{pmatrix} \textbf{q} \\ q_w \end{pmatrix} $ with $ \textbf{q} =  ( q_x, q_y, q_z)^T $. For attitude representation, the quaternion must satisfies a single constraint given by  $|| \mathbi{q} || = 1$.The quaternion kinematics equation in discrete-time is given by :

>>>>

\documentclass[twocolumn]{bmcart}

\usepackage[utf8]{inputenc} %unicode support

\usepackage{graphics} % for pdf, bitmapped graphics files
\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{subcaption}

\startlocaldefs

\endlocaldefs

%%% Begin ...
\begin{document}

%%% Start of article front matter
\begin{frontmatter}

\begin{fmbox}
\dochead{Research}

\author[
   addressref={aff1},                   % id's of addresses, e.g. {aff1,aff2}
   corref={aff1},     
   noteref={n1},                        % id's of article notes, if any
   email={nizar.ouarti@ipal.cnrs.fr}   % email address
]{\inits{NO}\fnm{Nizar} \snm{Ouarti}}
\author[
   addressref={aff1},   corref={aff1},  
   email={braud.thomas@ipal.cnrs.fr}
]{\inits{TB}\fnm{Thomas} \snm{Braud}}
\author[
   addressref={aff1},   corref={aff1},  
   email={vivien.billaud@ipal.cnrs.fr}
]{\inits{VB}\fnm{Vivien} \snm{Billaud}}

\address[id=aff1]{%                           % unique id
  \orgname{IPAL (Sorbonne UPMC, CNRS, Astar, NUS, UJF, IMT)}, % university, etc
  \city{Singapore}
  }

\end{fmbox}% comment this for two column layout

 \title{OpenMotion: An open source library for attitude estimation.}

@@

\begin{abstractbox}

\begin{abstract} % abstract

The abstract goes here
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% The keywords begin here                  %%
%%                                          %%
%% Put each keyword in separate \kwd{}.     %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{keyword}
\kwd{IMU}
\kwd{Sensor Fusion}
\kwd{Sensor Calibration}
\end{keyword}

\end{abstractbox}

\end{frontmatter}

@@

\texttt{OpenMotion} est une librairie open source qui permet a l'utilisateur d'estimer l'orientation du telephone a partir des donnee de l'IMU. La librairie ne supporte pas encore les translations, nous nous sommes concentre sur l'attitude.

@@

\item The object-fixed reference frame $\{c\}$ is a moving and rotating coordinate frame that is fixed to the smartphone device. 
\end{itemize}

The library admit admit that all the components of the IMU belong to the same reference frame $\{c\}$ (ref figure~\ref{Schema_situation}). It is a cyclopean approximation \cite{ouarti2008multimodal} .

@@

La librairie donne une estimation le quaternion $\mathbi{q}_a^c$

@@

A quaternion is a four-dimensional vector, defined as

\begin{center}
$ \mathbi{q} = \begin{pmatrix} \textbf{q} \\ q_w \end{pmatrix} $ with $ \textbf{q} =  ( q_x, q_y, q_z)^T $. 
\end{center}

For attitude representation, the quaternion must satisfies a single constraint given by  $|| \mathbi{q} || = 1$.The quaternion kinematics equation in discrete-time is given by :
